---
title: "Getting Started with omniAPIr"
author: "Your Name"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with omniAPIr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 6,
  fig.height = 4
)
```

# Introduction

`omniAPIr` provides a unified interface to multiple international data APIs. This vignette shows you how to get started with the most common use cases.

## Installation and Setup

```{r install, eval = FALSE}
# Install the package
devtools::install_github("yourusername/omniAPIr")

# Load the package
library(omniAPIr)
```

## Discovering Available APIs

First, let's see what APIs are available:

```{r api-info}
# View all available APIs
api_info <- get_api_info()
head(api_info[, c("api_name", "function_name", "requires_auth")])
```

## Discovering Indicators and Metadata

### UN Data Sources

For UN data sources (WHO, ILO, UNSDG, UNDP), use `list_un_indicators()`:

```{r un-indicators, eval = FALSE}
# List WHO indicators
who_indicators <- list_un_indicators("WHO")
head(who_indicators)

# Search for specific indicators
unemployment_indicators <- list_un_indicators("ILO", search = "unemployment")
```

### FAOSTAT Metadata

For FAO data, use `list_faostat_metadata()`:

```{r faostat-metadata, eval = FALSE}
# List available databases
databases <- list_faostat_metadata("databases")
head(databases)

# List elements for Crops and Livestock database
elements <- list_faostat_metadata("elements", database = "QCL")
head(elements)

# List items for Crops and Livestock database
items <- list_faostat_metadata("items", database = "QCL")
head(items)
```

## Fetching Data

### FAOSTAT Data

```{r faostat-data, eval = FALSE}
# Get cattle population data
cattle_data <- get_faostat_data(
  element = "2111",  # Stocks
  item = "cattle",
  database = "QCL",
  iso3 = "USA",
  mrv = 10
)

head(cattle_data)
```

### UN Data

```{r un-data, eval = FALSE}
# Get WHO data
who_data <- get_who_data(
  indicator = "WHOSIS_000001",
  mrv = 5
)

# Get ILO data
ilo_data <- get_ilo_data(
  iso3 = "USA",
  indicators = "UNE_DEAP_SEX_AGE_RT_A",
  mrv = 5
)
```

### World Bank Data (Requires Python)

```{r wb-data, eval = FALSE}
# Requires Python conda environment
wb_data <- get_wb_data(
  indicators = "SP.POP.TOTL",
  mrv = 5,
  conda_env = "your_env_name"
)
```

## Common Parameters

All data fetching functions use consistent parameters:

- `iso3`: ISO3 country code (e.g., "USA", "KEN")
- `mrv`: Most Recent Values - number of years to retrieve
- `verbose`: Print detailed progress messages
- `max_retries`: Number of retry attempts for failed requests

## Error Handling

The package includes comprehensive error handling:

```{r error-handling, eval = FALSE}
# Invalid country code
tryCatch({
  get_faostat_data(
    element = "2111",
    item = "cattle", 
    database = "QCL",
    iso3 = "INVALID"
  )
}, error = function(e) {
  message("Error: ", e$message)
})
```

## Next Steps

- Explore the full documentation with `?get_api_info()`
- Check the README for complete examples
- Run tests with `devtools::test()`
- Report issues on GitHub

For more detailed examples, see the package documentation and README file.